Supplemental Materials for \\ Helixer: Cross-species Gene Annotation of Large Eucaryotic Genomes Using Deep Learning

### 2020-06-04 paper/supplements.tex
minor things
animals first in coverage, authors to match main

\author[1]{Felix Stiehler}
\author[1]{Alisandra Denton}
\author[1]{Marvin Steinborn}
\author[ \hspace{-1ex}]{Daniela Dey}
\author[ \hspace{-1ex}]{Stephan Scholz}
\author[1]{Andreas Weber}
\affil[1]{Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

@@

All of the raw metadata and the four derived features mentioned above can be found in 
Dataset S\ref{supdata:metadata}).

@@

\begin{figure}[!h]
%\renewcommand\thefigure{S12}
\label{supfig:each_sp_vs_augustus}
\centerline{\includegraphics[]{images/cov_examples/each_sp_vs_augustus}}
\caption{
Fraction of bp with color-indicated a, c, e, g, i, k) coverage and b, d, f, h, j, l) spliced coverage of genomic positions
broken down by the confusion matrix of Augustus' and Helixer's predictions. Categories
are only displayed if they can be meaningfully compared by examining coverage or spliced
coverage. The rows show the individual species: a, b) {\it M. esculenta}, c, d) {\it M. truncatula}, 
e, f) {\it T. cacao}, g, h) {\it P. anubis}, i, j) {\it E. caballus} and k, l) {\it P. marinus} . 
The left-most bars show cases where the two tools agree,
while the remaining bars show paired conflicts. ``Ntrn" stand
for intron, and ``IG" stands for intergenic.
}
\end{figure}

\begin{figure}[!h]
%\renewcommand\thefigure{S13}
\label{supfig:each_sp_vs_ref}
\centerline{\includegraphics[]{images/cov_examples/each_sp_vs_ref}}
\caption{
Fraction of bp with color-indicated a, c, e, g, i, k) coverage and b, d, f, h, j, l) spliced coverage of genomic positions
broken down by the confusion matrix of the reference and Helixer's predictions. Categories
are only displayed if they can be meaningfully compared by examining coverage or spliced
coverage. The rows show the individual species: a, b) {\it M. esculenta}, c, d) {\it M. truncatula}, 
e, f) {\it T. cacao}, g, h) {\it P. anubis}, i, j) {\it E. caballus} and k, l) {\it P. marinus} . 
The left-most bars show cases where the two tools agree,
while the remaining bars show paired conflicts. ``Ntrn" stand
for intron, and ``IG" stands for intergenic.
}
\end{figure}

>>>>

\author[1]{Felix Stiehler}
\author[1]{Marvin Steinborn}
\author[ \hspace{-1ex}]{Stephan Scholz}
\author[ \hspace{-1ex}]{Daniela Dey}
\author[1]{Andreas P.M. Weber}
\author[1]{Alisandra K. Denton}
\affil[1]{Institue for Plant Biochemistry, Heinrich-Heine-University, Dusseldorf, D-40225, Germany}

@@

All of the raw metadata and the four derived features mentioned above can be found in 
Table S\ref{supdata:metadata}.

@@

\begin{figure}[!h]
%\renewcommand\thefigure{S12}
\label{supfig:each_sp_vs_augustus}
\centerline{\includegraphics[]{images/cov_examples/each_sp_vs_augustus}}
\caption{
Fraction of bp with color-indicated a, c, e, g, i, k) coverage and b, d, f, h, j, l) spliced coverage of genomic positions
broken down by the confusion matrix of Augustus' and Helixer's predictions. Categories
are only displayed if they can be meaningfully compared by examining coverage or spliced
coverage. The rows show the individual species: a, b) {\it P. anubis}, c, d) {\it E. caballus}, e, f) {\it P. marinus}, 
g, h) {\it M. esculenta}, i, j) {\it M. truncatula}, and k, l) {\it T. cacao}.
The left-most bars show cases where the two tools agree,
while the remaining bars show paired conflicts. ``Ntrn" stand
for intron, and ``IG" stands for intergenic.
}
\end{figure}

\begin{figure}[!h]
%\renewcommand\thefigure{S13}
\label{supfig:each_sp_vs_ref}
\centerline{\includegraphics[]{images/cov_examples/each_sp_vs_ref}}
\caption{
Fraction of bp with color-indicated a, c, e, g, i, k) coverage and b, d, f, h, j, l) spliced coverage of genomic positions
broken down by the confusion matrix of the reference and Helixer's predictions. Categories
are only displayed if they can be meaningfully compared by examining coverage or spliced
coverage. The rows show the individual species: a, b) {\it P. anubis}, c, d) {\it E. caballus}, e, f) {\it P. marinus}, 
g, h) {\it M. esculenta}, i, j) {\it M. truncatula}, and k, l) {\it T. cacao}. 
The left-most bars show cases where the two tools agree,
while the remaining bars show paired conflicts. ``Ntrn" stand
for intron, and ``IG" stands for intergenic.
}
\end{figure}
